5D de-aliased seismic data interpolation using non-stationary prediction error filter

### 2021-10-17 npef/paper.tex
Sun Oct 17 10:41:06 CDT 2021

%\begin{figure}[htb!]
%   \centering
%   \subfloat[]{\includegraphics[width=\textwidth]{real5dos/Fig/os_obs}
%   \label{fig:os_obs}}\\
%   \subfloat[]{\includegraphics[width=\textwidth]{real5dos/Fig/os_recon}
%   \label{fig:os_recon}}\\
%   \subfloat[]{\includegraphics[width=\textwidth]{real5dos/Fig/ts_recon}
%   \label{fig:ts_recon}}
%\caption{\new{Comparison between the two-step and one-step interpolation strategies. (a) Observed data when binned onto the regular grids of two times denser. (b) Reconstructed data by the one-step rank-reduction interpolation strategy. (c) Reconstructed data by the two-step rank-reduction and NPEF interpolation strategy.}  }
%\label{fig:os_obs,os_recon,ts_recon}
%\end{figure}

>>>>

\begin{figure}[htb!]
  \centering
  \subfloat[]{\includegraphics[width=\textwidth]{real5dos/Fig/os_obs}
  \label{fig:os_obs}}\\
  \subfloat[]{\includegraphics[width=\textwidth]{real5dos/Fig/os_recon}
  \label{fig:os_recon}}\\
  \subfloat[]{\includegraphics[width=\textwidth]{real5dos/Fig/ts_recon}
  \label{fig:ts_recon}}
\caption{\new{Comparison between the two-step and one-step interpolation strategies. (a) Observed data when binned onto the regular grids of two times denser. (b) Reconstructed data by the one-step rank-reduction interpolation strategy. (c) Reconstructed data by the two-step rank-reduction and NPEF interpolation strategy.}  }
\label{fig:os_obs,os_recon,ts_recon}
\end{figure}
